---
output: github_document
---

```{r, echo = FALSE}
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
version <- gsub('-', '.', version)
```
[![R-CMD-check](https://github.com/tsmodels/tsdistributions/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tsmodels/tsdistributions/actions/workflows/R-CMD-check.yaml)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/tsdistributions)](https://cran.r-project.org/package=tsdistributions)


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tsdistributions
A number of location-scale invariant distributions with full d,p,q,r methods 
and autodiff (TMB) backed estimation. These distributions are parameterized in
terms of the mean, standard deviation, skew and shape, with the GH distribution 
having 2 shape parameters.

The currently implemented distributions are shown below.


```{r,echo = FALSE,warning=FALSE,message=FALSE}
library(data.table)
references <- c("")
tab <- data.table(Distribution = c("Normal","Student","GED","Skew-Normal","Skew-Student","Skew-GED","Normal Inverse Gaussian","Generalized Hyperbolic",
                                   "Johnson's SU","Generalized Hyperbolic Skew Student"),
                  Function = c("norm","std","ged","snorm","sstd","sged","nig","gh","jsu","ghst"),
                  Parameters = c(2,3,3,3,4,4,4,5,4,4),
                  Notes = c(""," ","","Fernandez & Steel","Fernandez & Steel","Fernandez & Steel","Barndorff-Nielsen","Barndorff-Nielsen",
                            "Johnson","Aas & Haff")
                  )
tab <- knitr::kable(tab, format = "pipe", align = c("l","c","r"))
tab
```
